\documentclass[]{article}


% Title Page
\title{Drunk Detector App}
\author{George Strugnell and Toby Towler}

\begin{document}
	
\maketitle

\tableofcontents

\begin{abstract}
	
	Stuff
	
\end{abstract}

\section{Contribution}

	Contribution: 50 / 50 (equal)

\section{Aims, Motivation, Background}

	Real world problem we seek to solve. Description of similar systems (if any) and references to them. What are their pros and cons (how do we compare)
	500 words
	
\section{Sensing Section (System Architecture?)}

	What sensors are we using, and what for? What platform(s) are running our system, and why. How are the sensors linked with the system. What value does each sensor provide to our system, with regards to achieving the goal. Strengths and weaknesses of the sensors. What alternative approaches could have been used, and why have we chosen our current system
	600 words
	
\section{Data Collection Section (Data Collection?)}
	
	How has our data been collected, is it from a real world situation, mock scenario, or approximation. Justify collection method with strengths and weaknesses discussed. Give summary description of final dataset
	400 words

\section{Data Processing/Interpretation Section (Data Processing?)}
	
	How has the raw data been processed (data cleaning, feature engineering, modelling such as machine learning), and use of labelling/domain knowledge if relevant. Describe how it has been evaluated, and output of processing tested for reliability and accuracy (how did we test the results)
	600 words
	
\section{System Output and Feedback Section (System Output?)}

	Describe the outputs of the system that serve as feedback to the user, and any lo-fi diagrams. Give reasoning for these choices, with strengths and weaknesses. If user testing was done, this should be discussed.
	500 words
	
\section{Conclusion Section (Conclusion?)}

	Concluding overview of system. Summarise merits and shortcomings in relation to testing/evaluation done in each section, and in relation to the aim of the project.
	300 words
	
\appendix

\section{Appendix A: Code}

\section{Appendix B: Tables}

\bibliography{}
	Code, data tables, references, other listings go here
	Perhaps an appendix for code, an appendix for tables, and a references section.
\end{document}          
